---
title: "Untitled"
author: "Charlie Siciliano"
date: "2023-05-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(tidyverse)
gas_prices <- read.csv("gasoline_prices.csv")
state_codes <- read.csv("state_abb_codes.csv")
census_regions <- read.csv("censusRegions.csv")
StateCode_GasPrice <- merge(state_codes, gas_prices, by=c("State"))
##merging the data to see both the sate codes and prices by state 
type_gas <- c("Code", "Regular", "Diesel")
gp_name <- StateCode_GasPrice[type_gas]
gp_name
```

##Created a data frame that links the state code name and the corresponding regular and diesel prices.

```{r}
gp_ByRegion <- merge(gp_name, census_regions, by.x = "Code", by.y = "State")
gp_ByRegion
glimpse(gp_ByRegion)
```

##this table shows the prices and the code names, but then also includes the regions(N,E,S,W)

##in order to remove wahsington D.C...

gp_ByRegion_NoDC <- gp_ByRegion %>% filter(Code !="DC")

##For the result: group the data by region. That way it is easier to read. Include the percent increase between diesel and Regular and find the Standard deviation as well.

```{r}
gp_ByRegion_NoDC <- gp_ByRegion %>% filter(Code !="DC")
Result <- gp_ByRegion_NoDC %>% group_by(Region) %>%
summarise(mean_pct_increase = mean((Diesel - Regular)/Regular*100),
sd_pct_increase = sd((Diesel - Regular)/Regular*100),
coef_pct_increase = (sd((Diesel - Regular)/Regular*100)) / (mean((Diesel - Regular)/Regular*100)))
Result 
glimpse(Result)
```


